---
title       : Melbourne House Prices Map Application
subtitle    : an Application to find House Prices in Melbourne, Australia
author      : Paolo Coraggio
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, ]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
logo        : MelbourneLogo.png
assets      : {assets: ../../assets}
---

<style>
.title-slide {
  background-color: #FF8A00; /* #EDE0CF; ; #CA9F9D*/
}
</style>

--- .class #id bg:black

## HPM App 

1. The application shows houses prices in Melbourne
2. Shows an interactive map
3. Allow you to search using customisable parameters

--- .class #id bg:black

## How to use it

> Go to the Map section of the application

> Insert the parameters of your search

> The resulting matches are shown on a Map with additional information

> Compare the price of the houses with the mean of Melbourne House Market

--- .class #id 

## How to push on Git?


a. I simply don't know..
b. RAAAAAAAA

--- .class #id 

## A Simple Plot

```{r simpleplot, fig.height=6, fig.align='center', message = FALSE}
require(ggplot2)
qplot(wt, mpg, data = mtcars)
```

--- .class #id bg:yellow

## Motion plot

```{r, results = 'asis', comment=NA, message = FALSE, echo=FALSE}
require(googleVis)
M1 <- gvisMotionChart(Fruits, idvar="Fruit", timevar = "Year")
print(M1, tag = 'chart')
```


--- .class #id 

## Interactive Chart

require(rC)